Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs

### 2019-03-06 writing/IC2S2_abstract/IC2S2_abstract.tex
added subfolder structure, made plots work.

\title{Decentralized Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}

@@

We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to monopolies. 
In this work, we show that a good trade-off is based on the integration of two rather unusual concepts:
\begin{enumerate}[(i),topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]

@@

	\item and a idiosyncratic buyer-seller transaction cost.

@@

Through tuning of $\gamma$ and targeted redistribution of tax money from transaction costs, we show that this model is able to fuel a self-consistent economy, 
with fair competition, where innovations can spread across the topology freely, but without the chance of monopolies emerging through disproportional feedback mechanisms.

\red{
@Sandy: We are thinking of replacing the `Decentralized' in the title by something like `balanced', to avoid false association with over-hyped blockchain technology.
What are your thoughts?
}

>>>>

\title{Fair, Stable Exchange Networks through Quenched Merchant Location and Idiosyncratic Trading Costs}

@@

We conclude that geographical constraints can lead to unfair and inefficient conditions for the customers, whereas removal of those constraints can lead to monopolies. 
In this work, we show that we can avoid both unfairness and monopolies at relatively small cost based on two rather unusual concepts:

\begin{enumerate}[(i),topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]

@@

	\item and an idiosyncratic buyer-seller transaction cost.

@@

Through tuning of $\gamma$ and targeted redistribution of tax money to regions of low economic activity, we show that this model is able to fuel a self-consistent economy, 
with fair competition, where innovations can spread across the topology freely, but without the chance of monopolies emerging through disproportional feedback mechanisms. 
In summary, we present a model that avoids the winner-take-all monopoly tendency and associated negative externalities of today's internet enabled business through a low cost tax based on a topological constraint.
